Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-08-20 xrb2/paper.tex
add some figure descriptions

\begin{figure}[t]
\centering
\plotone{time_series_500}
\caption{Time series of the 500 Hz run showing $\bar{A}$.}
\end{figure}

\begin{figure}[t]
\centering
\plotone{time_series_1000}
\caption{Time series of the 1000 Hz run showing $\bar{A}$.}
\end{figure}

@@

different initial models?

@@

look at flame speed, shape of flame, amount of mixing (e.g. it looks like slower rotation rates have less mixed flames as the hurricane is less strong.)

\begin{figure}[t]
	\centering
	\plottwo{speeds_1_100th_max.pdf}{speeds_1_1000th_max.pdf}
	\caption{Plots of flame front position vs.\ time for the 500 Hz and 1000 Hz runs. The left-hand plot shows the results when tracking the $\frac{1}{100} \max[\enucdot]$ contour, while the right-hand plot shows the results for the $\frac{1}{1000} \max[\enucdot]$ contour.}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\plotone{time_series_500}
\caption{\label{fig:time_series_500} Time series of the 500 Hz run showing $\bar{A}$.}
\end{figure}

\begin{figure}[t]
\centering
\plotone{time_series_1000}
\caption{\label{fig:time_series_1000} Time series of the 1000 Hz run showing $\bar{A}$.}
\end{figure}

Figures~\ref{fig:time_series_500} and \ref{fig:time_series_1000} show
time series of the mean molecular weight for the 500~Hz and 1000~Hz
runs.  Compared to those in \cite{flame_wave1}, ashes behind the flame
do not reach as high atomic weights.  This is not surprising, since
those early runs boosted the reaction rates.  Comparing these two new
runs, we see that the burning is much more evolved for the higher
rotation rate.  We believe that this is because the rotation confines
the initial perturbation and subsequent expansion from the burning
better, allowing the reactions to progress further.

@@

@@

shape of flame, amount of mixing (e.g. it looks like slower rotation rates have less mixed flames as the hurricane is less strong.)

Figure~\ref{fig:flame_speeds} shows the position of the flame as a
function of time.  Defining the position is difficult, so we \MarginPar{need explanation here}

\begin{figure}[t]
	\centering
	\plottwo{speeds_1_100th_max.pdf}{speeds_1_1000th_max.pdf}
	\caption{\label{fig:flame_speeds} Plots of flame front position vs.\ time for the 500 Hz and 1000 Hz runs. The left-hand plot shows the results when tracking the $\frac{1}{100} \max[\enucdot]$ contour, while the right-hand plot shows the results for the $\frac{1}{1000} \max[\enucdot]$ contour.}
\end{figure}
